%-------------------------
% Resume in LaTeX
% Author : Patrick Pei
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Patrick Pei} & Email: \href{mailto:yingjianpei2022@u.northwestern.edu}{yingjianpei2022@u.northwestern.edu}\\
  \href{https://github.com/peiyj}{github.com/peiyj} & Mobile: \href{tel:+18586665517}{+1-858-666-5517} \\
  \href{https://linkedin.com/in/patrickpei11}{linkedin.com/in/patrickpei11} & \\
\end{tabular*}

\vspace{4pt}
\small{Senior Software Engineer building AI-powered products and scalable distributed systems at Coursera. Specializing in LLM application development, prompt engineering, and enterprise-scale AI integration.}

%-----------AI PROJECTS-----------------
\section{AI Projects}

  \resumeSubheading
    {AI-Powered Curation Builder Platform}{Coursera}
    {Lead Engineer}{2024 -- Present}
    \resumeItemListStart
      \resumeItem{Prompt Architecture}
        {Architected a template-based prompt system with 6+ specialized prompt executors for program outlines, domain queries, content suggestions, and collection filtering using OpenAI GPT-4.1.}
      \resumeItem{Multimodal Processing}
        {Implemented multimodal document processing --- PDF/DOCX uploads converted to images via PDFBox/POI for vision-capable LLM prompts with signed S3 URLs.}
      \resumeItem{Production LLM Integration}
        {Built structured JSON output parsing with retry logic and fault tolerance for reliable LLM response handling. Migrated from Azure OpenAI to native OpenAI client with Spring Retry-based resilience patterns.}
      \resumeItem{AI Content Pipeline}
        {Designed AI-ranked content suggestion pipeline integrating product search APIs with LLM-based relevance filtering for enterprise learning program curation.}
    \resumeItemListEnd

  \resumeSubheading
    {AI Developer Tooling \& Workflows}{Personal}
    {Builder}{2024 -- Present}
    \resumeItemListStart
      \resumeItem{MCP Integration}
        {Integrate and configure MCP (Model Context Protocol) servers for connecting AI assistants to external tools, APIs, and data sources.}
      \resumeItem{Agent Frameworks}
        {Design reusable agent skills and prompt frameworks for structured AI-assisted development workflows including brainstorming, debugging, code review, and TDD.}
      \resumeItem{AI-Assisted Development}
        {Leverage AI coding agents daily for full-cycle software development --- from architecture design through implementation and testing.}
    \resumeItemListEnd

%-----------EXPERIENCE-----------------
\section{Experience}

  \resumeSubheading
    {Coursera}{Mountain View, CA}
    {Senior Software Engineer}{Mar 2024 -- Present}
    \resumeItemListStart
      \resumeItem{AI-Powered Curation Platform}
        {Led a team of 5 engineers to design and build an AI-powered content curation platform using OpenAI GPT-4.1 with multimodal prompt engineering, structured output parsing, and production-grade LLM service integration for enterprise learning program creation.}
      \resumeItem{Badge Management Platform}
        {Architected a stream-processing system for real-time badge issuance serving all enterprise organizations, contributing to over \$10M in contract ACVs.}
      \resumeItem{Technical Leadership}
        {Lead a team of 3--4 engineers designing and shipping enterprise-scale platforms for contract management and badge issuance across Coursera's B2B product line.}
      \resumeItem{Allowlist Management Platform (P0)}
        {Led P0 project with 4 engineers, reducing contract-level course update time from 2 weeks to under 10 seconds through near real-time data pipelines.}
      \resumeItem{Internal Tooling}
        {Built conflict detection workflows with Apache Airflow; launched Retool-based internal platform cutting engineering ops time from 95 minutes to under 5 seconds.}
    \resumeItemListEnd

  \resumeSubSubheading
    {Software Engineer II}{Mar 2023 -- Mar 2024}
    \resumeItemListStart
      \resumeItem{Clips Management Platform}
        {Led team of 3 engineers architecting fault-tolerant distributed system for clips metadata management. Enabled parallel processing reducing update time by 80\%.}
      \resumeItem{Performance Engineering}
        {Implemented distributed Redis cache reducing P95/P99 read latency by 80\%/92\%. Designed application-level transactions ensuring data integrity for downstream services.}
    \resumeItemListEnd

  \resumeSubSubheading
    {Software Engineer I}{Jan 2022 -- Mar 2023}
    \resumeItemListStart
      \resumeItem{Migration Platform}
        {Led Scala-to-Java service migrations, deprecating 12 legacy APIs and \textasciitilde5K lines of code. Built gRPC microservices handling \textasciitilde3K QPS with 98\% test coverage.}
      \resumeItem{Reusable Migration Library}
        {Created migration library with automated dual read/write, adopted by 4 teams across 15 migrations.}
    \resumeItemListEnd

  \vspace{4pt}
  \resumeSubheading
    {Samsara}{San Francisco, CA}
    {Software Engineering Intern}{Jun 2021 -- Oct 2021}
    \resumeItemListStart
      \resumeItem{Config Pusher Optimization}
        {Optimized Config Pusher System using Go's fan-in concurrency pattern, reducing P95 latency by 90\% through request batching with in-memory queue.}
    \resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubheading
    {Northwestern University}{Evanston, IL}
    {Master of Science in Computer Engineering, GPA: 4.0/4.0}{Sep 2020 -- Dec 2021}
  \vspace{4pt}
  \resumeSubheading
    {University of California, San Diego}{La Jolla, CA}
    {Bachelor of Science in Computer Engineering, GPA: 3.7/4.0}{Sep 2016 -- Jun 2020}

%--------SKILLS------------
\section{Technical Skills}
  \begin{itemize}[leftmargin=*, itemsep=1pt, parsep=0pt, topsep=0pt]
    \item \textbf{AI \& LLM:} OpenAI API, GPT-4.1, Prompt Engineering, Structured Output Parsing, Multimodal AI, MCP (Model Context Protocol), AI Agent Frameworks
    \item \textbf{Languages:} Java, Python, Go, JavaScript, TypeScript, SQL, C++
    \item \textbf{Backend \& Data:} Spring Boot, gRPC, GraphQL, Kafka, Redis, PostgreSQL, DynamoDB, MySQL, MongoDB, Airflow, Elasticsearch
    \item \textbf{Cloud \& Infrastructure:} AWS (EKS, Lambda, MSK, DynamoDB, S3, Aurora), Docker, Kubernetes, Terraform, GitHub Actions, Jenkins
  \end{itemize}

%-------------------------------------------
\end{document} 